CONEM2024-0025\\ ABC MULTICRITERIA CLASSIFICATION WITH ANALYTICAL HIERARCHY PROCESS: HOW TO FORCE CONSISTENCY OF PAIRWISE COMPARISONS MATRIX

### 2024-02-05 accepted/CONEM2024/FCPCOM/CONEM2024.tex
complement

	The solution that we adopted in this work for multicriteria classification with lead time and billing criteria, was inspired on the work of Willians. A single measure was adopted for these two criteria (lead time billing) dividing the billing by the complement of the lead time percentage.

@@

$e_{p\sigma_q}$ is the product lead time billing weight percentage equivalent to product $p$ on the criterion $\sigma_q$;

@@

$\frac{b_p}{1 + (lt^{\max} - lt_p)}$ is the lead time billing weight percentage of product $p$;

>>>>

	The solution that we adopted in this work for multicriteria classification with lead time and billing criteria, was inspired on the work of Willians. A single measure was adopted for these two criteria (lead time billing weight complement) dividing the billing by the complement of the lead time percentage.

@@

$e_{p\sigma_q}$ is the product lead time billing weight percentage complement equivalent to product $p$ on the criterion $\sigma_q$;

@@

$\frac{b_p}{1 + (lt^{\max} - lt_p)}$ is the lead time billing weight percentage complement for product $p$;
